### 2014-10-16 fundamentals/intro.tex
cleaning up

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables major capabilities that previous 
simulators lack. First, its \emph{modular and open architecture}  facilitates 
targeted contribution and collaboration within the nuclear fuel cycle analysis 
community.  Additionally, \emph{agent interchangeability} facilitates direct 
comparison of modeling methodologies. Finally, the flexibility and generality 
of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
emphasizes applicability of the \Cyclus tool across a broader range of 
applications than other simulators.

Modeling the evolution of a physics-dependent, international nuclear fuel supply
chain is a multiscale problem. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition fast reactor fuel. Accordingly, each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels either impossible or difficult and time consuming.

@@

@@

We expect that there are a number of types of users and developers who will 
interact with the \Cyclus framework. Those people fall into a number of 
categories. All such people benefit from the modular architecture.

>>>>

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables major capabilities that previous 
simulators lack. First, its its \emph{modular and open architecture}  facilitates 
targeted contribution and collaboration within the nuclear fuel cycle analysis 
community.  Additionally, \emph{agent interchangeability} facilitates direct 
comparison of modeling methodologies. Finally, the flexibility and generality 
of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
emphasizes applicability of the \Cyclus tool across a broader range of 
fidelities, scales, and applications than other simulators.

@@

Furthermore, modeling the evolution of a physics-dependent, international nuclear fuel supply
chain is a multiscale problem, but existing tools are not sufficiently 
multi-scale. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition fast reactor fuel. Accordingly, each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels either impossible or difficult and time consuming. 
However, an extensible architecture and discrete object tracking allow 
the creation and exchange ability of custom \Cyclus archetypes at any level of fidelity.

@@

We expect that there are a number of types of users and developers who will 
interact with the \Cyclus framework. National laboratory researchers,
graduate student and faculty researchers  Those people fall into a number of 
categories. All such people benefit from the modular architecture.
